\documentclass[a4paper,9pt]{article}
\usepackage{fullpage}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{verbatim}
\usepackage{a4wide}
\usepackage[T1]{fontenc}
\usepackage{lmodern}            % scalable fonts (needed by microtype expansion)
\usepackage{CV}
\usepackage{amstext}
\usepackage{enumitem}
\usepackage{microtype}          % subtle spacing/justification improvements
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{marvosym}
\usepackage{academicons}

\hypersetup{breaklinks=true, pagecolor=white, colorlinks=true, citecolor=blue, linkcolor=black, urlcolor=black}
\urlstyle{rm} % suppresses typewriter font for url

% Tighter, consistent lists throughout
\setlist[itemize]{leftmargin=1.5em, itemsep=2pt, topsep=2pt, parsep=0pt}

% Uniform spacing between publication / working-paper entries
\newcommand{\cvgap}{\vspace{2mm}}

\fancyhead[L]{\small{\emph{Curriculum Vitae}}}
\fancyhead[C]{\Large{\textsc{Francisco Cavalcanti}}}
\fancyhead[R]{\small{\emph{\today}}}
\pagestyle{fancy}
\setlength{\headheight}{16pt}
\begin{document}
\vspace*{0.1mm}
\normalsize

\section{Personal Info}

\begin{flushleft}
\begin{tabular}{lll}
\faGlobe\ \href{https://franciscocavalcanti.github.io}{franciscocavalcanti.github.io}   &\hspace{2mm} \Letter\hspace{0.2mm} \href{mailto:francisco.dlcavalcanti@ufpe.br}{\nolinkurl{francisco.dlcavalcanti@ufpe.br}}  &\hspace{2mm} \\
\end{tabular}
\end{flushleft}

\section{Positions}

\begin{flushleft}
\begin{tabular}{ll}
\textbf{Assistant Professor at the \href{https://www.ufpe.br/decon}{Department of Economics at UFPE} (2023 -- present)} \\
Post-doctoral researcher at the \href{http://www.econ.puc-rio.br/}{Department of Economics at PUC-Rio} (2018 -- 2023) \\
Operational coordinator at \href{http://www.econ.puc-rio.br/datazoom/index.html}{Data Zoom} (2019 -- 2023) \\
\end{tabular}
\end{flushleft}

\section{Education}

\begin{itemize}

\item{\textbf{Ph.D.} \emph{excellent cum laude} in Economics at \href{http://www.ub.edu/school-economics/}{University of Barcelona} (2018). \\ Visiting Ph.D student at \href{https://warwick.ac.uk/fac/soc/economics/}{University of Warwick} (UK) -- Fall 2016. \\ Supervisors: Amedeo Piolatto, Albert Sol\'e-Oll\'e.}

\item{\textbf{Master} in Economics at \href{https://sites.google.com/view/pimes/principal}{PIMES/UFPE} (2013). Supervisor: Raul Silveira-Neto.}

\item{\textbf{Bachelor} in Economics at \href{https://www.ufpe.br/ccsa/}{Federal University of Pernambuco} (2010).}

\end{itemize}

\section{Selected Publications}

\textbf{\href{https://doi.org/10.1016/j.jebo.2025.106998}{Natural Disasters and Voting Behavior Under Authoritarian Regimes: Evidence From the Brazilian Shrimp Vote.}} \emph{Journal of Economic Behavior \& Organization, 2025}, Vol.~234, p.~106998. (with D.~Baerlocher, R.~Caldas \& R.~Schneider)

\cvgap

\textbf{\href{https://onlinelibrary.wiley.com/doi/full/10.1111/obes.12560}{Drought-Reliefs and Partisanship.}} \emph{Oxford Bulletin of Economics and Statistics, 2024}, Vol.~86, p.~187--208. (with \href{https://sites.google.com/site/federicoboffaunibz/}{F.~Boffa}, \href{https://sites.google.com/site/piolatto/home}{A.~Piolatto} \& \href{https://sites.google.com/site/cfonsrosen/home}{C.~Fons-Rosen}) \\
\hspace{2em} \href{https://voxeu.org/article/insights-distributive-politics-new-way-measure-aridity}{VoxEU: New insights on distributive politics from a new way to measure aridity} \\
\hspace{2em} \href{https://github.com/FranciscoCavalcanti/Drought-reliefs-and-Partisanship}{GitHub repository}

\cvgap

\textbf{\href{https://www.sciencedirect.com/science/article/pii/S0047272718301361}{Popularity Shocks and Political Selection.}} \emph{Journal of Public Economics, 2018}, Vol.~165, p.~201--216. (with \href{http://www.gianmarcodaniele.com/}{G.~Daniele} \& \href{http://sergio-galletta.com/}{S.~Galletta})

\section{Working Papers}

\textbf{\href{https://www.researchgate.net/profile/Francisco-Cavalcanti-6/publication/406502168_Education_and_Job_Loss_During_COVID-19_Evidence_from_Brazil/links/6a29d64a68552924bb0049a2/Education-and-Job-Loss-During-COVID-19-Evidence-from-Brazil.pdf}{Education and Job Loss During COVID-19: Evidence from Brazil.}} (with F.~Didier \& G.~Gonzaga)

\cvgap

\textbf{\href{https://ideas.repec.org/p/usf/wpaper/2026-01.html}{Beyond Appearance: The Socioeconomic and Historical Roots of Racial Identity in Brazil.}} \emph{University of South Florida, Department of Economics Working Papers, 2026.} (with D.~Baerlocher \& R.~Caldas)

\cvgap

\textbf{\href{https://economics.ucr.edu/docs/helfand/Helfand\%20Determinants\%20of\%20Total\%20Factor\%20Productivity\%20Growth\%20\%20draft\%2010-2025.pdf}{Total Factor Productivity Growth in Brazilian Agriculture (1985--2017): The Roles of Climate Change and Public Policy.}} \emph{IDB Working Paper, 2025.} (with S.~Helfand, C.~de Freitas \& A.~Moreira)

\cvgap

\textbf{\href{https://www.researchgate.net/profile/Ricardo-Carvalho-10/publication/383129940_Do_Landslides_Impact_Urbanization_Patterns_Evidence_from_Brazilian_Cities/links/66be0c688d0073559255b1e4/Do-Landslides-Impact-Urbanization-Patterns-Evidence-from-Brazilian-Cities.pdf}{Do Landslides Impact Urbanization Patterns? Evidence from Brazilian Cities.}} (2024, with R.~Lima, P.~Alves \& B.~Barsanetti)

\cvgap

\textbf{\href{https://economics.ucr.edu/docs/helfand/Helfand\%20Climate\%20Change,\%20Drought,\%20and\%20Ag\%20Prod\%20in\%20Brazil\%208-2024.pdf}{Climate Change, Drought, and Agricultural Production in Brazil.}} (with S.~Helfand \& A.~Moreira)

\cvgap

\textbf{\href{http://diposit.ub.edu/dspace/handle/2445/182602}{Ignorance is Bliss: Voter Education and Alignment in Distributive Politics.}} \emph{IEB Working Paper 2021/07, Institut d'Economia de Barcelona, 2021.} (with F.~Boffa \& A.~Piolatto)

\cvgap

\textbf{\href{https://mpra.ub.uni-muenchen.de/88317/}{Voters Sometimes Provide the Wrong Incentives: The Lesson of the Brazilian Drought Industry.}} (2018)

\cvgap

\textbf{\href{https://www.researchgate.net/publication/319902513_Creative_Class_Human_Capital_and_Urban_Dynamism_Empirical_Evidence_for_the_Brazilian_Cities}{Creative Class, Human Capital and Urban Dynamism: Empirical Evidence for the Brazilian Cities.}} \emph{Anais do XLII Encontro Nacional de Economia, No.~160, 2016.} (with R.~Silveira-Neto)

\section{Work in Progress}

\begin{itemize}
\item Droughts, Sanitation Provision, and Access to Services in Brazil (with T.~Soares \& P.~F.~Azevedo)
\item Mobile Broadband Expansion and Tasks: Evidence from Brazilian Formal Labor Markets (with H.~Mota \& G.~Gonzaga)
\item Drought and Corruption
\item Show Me Your Pix: The Impact of Electronic Payment Technologies on Tax Collection
\end{itemize}

\section{Grants and Scholarships}

\noindent \textbf{ESRC} UK-Brazil global talent exchange scheme (2025). \textbf{CAPES} -- post-doctoral fellow (2018 -- 2023). \textbf{GRANT} -- Ministry of Economy and Competitiveness / Government of Spain (ECO2015-68311-R). PI: Albert Sol\'e-Oll\'e (2016 -- 2018). \textbf{APIF} -- UB Ph.D Scholarship (2015 -- 2018). \textbf{IEB Ph.D Scholarship} -- Barcelona Economic Institute (2014 -- 2015). \textbf{GRANT} -- Ministry of Economy and Competitiveness / Government of Spain (ECO2012-37131). PI: Albert Sol\'e-Oll\'e (2013 -- 2015). \textbf{CNPq Scholarship} -- Ministry of Education of Brazil (2013 -- 2013). \textbf{CNPq Master Scholarship} -- Ministry of Education of Brazil (2011 -- 2013).

\clearpage
\vspace*{0.1mm}

\section{Conferences, Workshops, and Seminars}

\noindent \textbf{2025} Just Transition Hub (Dundee, UK), Liverpool School of Tropical Medicine (Liverpool, UK), University of York (York, UK). \textbf{2024} Society for Institutional \& Organizational Economics (SIOE) and Ronald Coase Institute Alumni Conference (Chicago, USA), PIMES/UFPE Economics Seminars (Recife, Brazil). \textbf{2023} PIMES/UFPE Economics Seminars (Recife, Brazil), PPGE/UFPB Economics Seminar (João Pessoa, Brazil). \textbf{2022} LACEA-LAMES (Lima, Peru). \textbf{2021} 2º Workshop AMZ 2030 (Belém, Brazil). \textbf{2020} FEA-USP Economics Seminars (Online), UCB Economics Seminars (Online). \textbf{2019} PIMES/UFPE Economics Seminars (Recife, Brazil), Ronald Coase Workshop on Institutional Analysis (Warsaw, Poland). \textbf{2018} Higher School of Economics (HSE) (Moscow, Russia), Carioca Workshop on Political Economy (Rio de Janeiro, Brazil), SBE -- Brazilian Econometric Society (Rio de Janeiro, Brazil). \textbf{2017} SAEe Spanish Economic Association (Barcelona, Spain), PIMES/UFPE Economics Seminars (Recife, Brazil), LACEA-LAMES (Buenos Aires, Argentina). \textbf{2016} CWIP Seminar / University of Warwick (Coventry, UK), Workshop on The Political Economy of Federalism and Local Development (Bruneck, Italy), Conference on Development Economics and Policy (Heidelberg, Germany), PIMES/UFPE Economics Seminars (Recife, Brazil), IEB Seminars (Barcelona, Spain), Lisbon Meeting on Institutions and Political Economy (Lisbon, Portugal). \textbf{2015} Workshop on PhD in Economics of UB (Barcelona, Spain), Summer School in Development Economics (Garda, Italy). \textbf{2014} VII Italian Doctoral Workshop in Empirical Economics (Turin, Italy), PIMES/UFPE Economics Seminars (Recife, Brazil), IEB Seminars (Barcelona, Spain).

\section{Academic and Research Activities}

\begin{flushleft}
\begin{tabular}{l}
\textbf{Referee Service}: Economia, British Journal of Political Science, The Economic Journal, \\
The Review of Economics and Statistics \\
\\
\textbf{Organizer Committee}: LACEA 2025 Annual Meeting, Micro Applied Seminar of PUC-Rio \\
(2019 -- 2020), Economics Ph.D Seminar of University of Barcelona (2014 -- 2016). \\
\end{tabular}
\end{flushleft}

\section{Teaching}

\begin{flushleft}
\begin{tabular}{lll}
\multicolumn{3}{l}{\textbf{Graduate}} \\
Student's Seminars & 2025 & UFPE \\
\\
\multicolumn{3}{l}{\textbf{Undergraduate}} \\
Economics of Climate Change & 2025 -- 2026 & UFPE \\
Monetary Economics & 2024 & UFPE \\
Microeconomics & 2024 & UFPE \\
Introduction to Economics & 2023 -- 2026 & UFPE \\
Political Economy & 2017 & University of Barcelona \\
Fundamentals of Taxation & 2015 -- 2017 & University of Barcelona \\
Macroeconomics & 2013 & UFPE \\
Macroeconomics & 2012 & UFRPE \\
\end{tabular}
\end{flushleft}

\clearpage
\vspace*{0.1mm}

\section*{Technical Reports and Other Publications}

\begin{flushleft}

\textbf{Análise das Desigualdades Socioeconômicas de Gênero e Raça e Políticas Públicas na Amazônia Brasileira.} Consultoría -- Proyecto RG-T3975: Desarrollo Sostenible de la Amazonía con Enfoque de Género y Diversidad, September 2025.

\cvgap

\textbf{\href{https://amazonia2030.org.br/desigualdades-no-mercado-de-trabalho-por-raca-evidencias-para-a-amazonia-legal/}{Desigualdades no Mercado de Trabalho por Raça: Evidências para a Amazônia Legal.}} (with Gustavo Gonzaga). Projeto Amazônia 2030, No.~42, June 2022, p.~42.

\cvgap

\textbf{\href{https://amazonia2030.org.br/desigualdades-no-mercado-de-trabalho-por-genero-evidencias-para-a-amazonia-legal/}{Desigualdades no Mercado de Trabalho por Gênero: Evidências para a Amazônia Legal.}} (with Gustavo Gonzaga). Projeto Amazônia 2030, No.~36, April 2022, p.~42.

\cvgap

\textbf{\href{https://amazonia2030.org.br/dinamismo-de-emprego-e-renda-na-amazonia-legal-ocupacoes-qualificadas-e-de-lideranca/}{Dinamismo de Emprego e Renda na Amazônia Legal: Ocupações Qualificadas e de Liderança.}} (with Flávia Alfenas \& Gustavo Gonzaga). Projeto Amazônia 2030, No.~15, August 2021.

\cvgap

\textbf{\href{https://amazonia2030.org.br/dinamismo-de-emprego-e-renda-na-amazonia-legal-servicos/}{Dinamismo de Emprego e Renda na Amazônia Legal: Setor Serviços.}} (with Flávia Alfenas \& Gustavo Gonzaga). Projeto Amazônia 2030, No.~14, August 2021.

\cvgap

\textbf{\href{https://amazonia2030.org.br/dinamismo-de-emprego-e-renda-na-amazonia-legal-setor-publico/}{Dinamismo de Emprego e Renda na Amazônia Legal: Setor Público.}} (with Flávia Alfenas \& Gustavo Gonzaga). Projeto Amazônia 2030, No.~13, August 2021.

\cvgap

\textbf{\href{https://amazonia2030.org.br/dinamismo-de-emprego-e-renda-na-amazonia-legal-agropecuaria/}{Dinamismo de Emprego e Renda na Amazônia Legal: Agropecuária.}} (with Flávia Alfenas \& Gustavo Gonzaga). Projeto Amazônia 2030, No.~10, August 2021.

\cvgap

\textbf{\href{https://amazonia2030.org.br/mercado-de-trabalho-na-amazonia-legal-uma-analise-comparativa-com-o-resto-do-brasil/}{Mercado de Trabalho na Amazônia Legal: Uma Análise Comparativa com o Resto do Brasil.}} (with Flávia Alfenas \& Gustavo Gonzaga). Projeto Amazônia 2030, November 2020, p.~68.

\cvgap

\textbf{Nível e Evolução da Desigualdade de Renda na Bahia: uma avaliação do papel da educação e dos programas sociais.} (with Rodrigo Oliveira). Bahia Análise \& Dados, v.~24, p.~89, 2014.

\end{flushleft}

\end{document}
